### 2020-05-05 README.Rmd

``` r
install.packages("devtools")
devtools::install_github("crsh/papaja", dependencies = TRUE)
devtools::install_github("cjvanlissa/worcs", dependencies = TRUE)
tinytex::install_tinytex()
worcs::git_credentials("your_name", "your_email")
```

>>>>

``` r
if(!requireNamespace("remotes"))install.packages("remotes")
remotes::install_github("crsh/papaja", dependencies = TRUE, update = "never")
remotes::install_github("cjvanlissa/worcs", dependencies = TRUE, update = "never")
tinytex::install_tinytex()
worcs::git_credentials("your_name", "your_email")
```
